---
title: "p8105_hw1_zh2494"
author: "zhuolun"
date: "9/23/2021"
output: github_document
---

# section 1
```{r message = FALSE}
library(tidyverse)
```

# section 2
```{r}
problem_1_df = tibble(
  vec_numeric = rnorm(n = 10),
  vec_logical = vec_numeric > 0,
  vec_char = c("a","b","c","d","e","f","g","h","I","g"),
  vec_factor = factor(c("high","low","median","high","low","median","high","low","median","high"))
)
problem_1_df

```

# section 3
```{r mean_of_all_variable}
mean_numeric = mean(pull(problem_1_df, vec_numeric))
mean_logical = mean(as.numeric(pull(problem_1_df, vec_logical)))
mean_char = mean(as.numeric(pull(problem_1_df, vec_char)))
mean_factor = mean(as.numeric(pull(problem_1_df, vec_factor)))
```

The mean of the numeric number is `r mean_numeric`
The mean of the numeric number is `r mean_logical`
The mean of the numeric number is `r mean_char`,the result is NA, because the charater is not converted to number. 
The mean of the numeric number is `r mean_factor`

# section 4

```{r}
# install.packages("palmerpenguins")
data("penguins", package = "palmerpenguins")
view(penguins)
mean(as.numeric(pull(penguins,flipper_length_mm)))
skimr::skim(penguins)
a = as.numeric(pull(penguins,flipper_length_mm))
a1 = a[!is.na(a)]
mean(a1)
```

• The names of the penguins are `r names(penguins)`
• The mean of the flipper length is `r mean(pull(penguins,flipper_length_mm))`
• The data frame penguins has `r nrow(penguins)` rows 
• The data frame penguins has `r ncol(penguins)` columns
• The mean flipper length is `r mean(a1)`

```{r}
ggplot(penguins, aes(x = bill_length_mm,y = flipper_length_mm,color = species)) + geom_point()

ggsave("scatter_plot.jpeg", height = 4, width = 4)
```




