---
title: "p8105_hw1_zh2494"
author: "zhuolun"
date: "9/23/2021"
output: github_document
---

```{r include = FALSE}
library(tidyverse)
library(ggplot2)
```

# problem 1

* create the data frame

```{r}
problem_1_df = tibble(
  vec_numeric = rnorm(n = 10), # a random sample of size 10 from a standard normal distrbution
  vec_logical = vec_numeric > 0, # a logical vector indicating whether elements of the sample are greater than 0
  vec_char = c("a","b","c","d","e","f","g","h","I","g"), # a character vector of length 10
  vec_factor = factor(c("high","low","median","high","low","median","high","low","median","high"))
) # a factor vector of length 10, with 3 different factor “levels”

# problem_1 data frame
problem_1_df 
```

* take the mean of each variables

```{r mean_of_all_variable}
#  a random sample of size 10 from a standard Normal distribution
mean_numeric = mean(pull(problem_1_df, vec_numeric))
mean_numeric
# a logical vector indicating whether elements of the sample are greater than 0
mean_logical = mean(pull(problem_1_df, vec_logical))
mean_logical
# a character vector of length 10
mean_char = mean(pull(problem_1_df, vec_char))
mean_char
# a factor vector of length 10, with 3 different factor “levels”
mean_factor = mean(pull(problem_1_df, vec_factor))
mean_factor
```

**The mean of the numeric number is `r mean_numeric`.**
**The mean of the mean_logical is `r mean_logical`.**
**The mean of the character is `r mean_char`,taking the mean does not work and will return NA**
**The mean of the factor number is `r mean_factor`,taking the mean does not work and will return NA**

* Add ``as.numeric` function to logical,character and factor variables

```{r, results="hide"}
# add as.numeric to nordist_sam
as.numeric(pull(problem_1_df ,vec_numeric))
# add as.numeric to sam_greater0
as.numeric(pull(problem_1_df ,vec_logical))
# add as.numeric to chara_10
as.numeric(pull(problem_1_df ,vec_char))
# add as.numeric to fact_10
as.numeric(pull(problem_1_df ,vec_factor))
```

**`as.numeric` is applied to logical variable and numeric variable.**
**but it can not be used for character and factor variable.**
**This the reason why the logical variable and numeric variable can be** **converted but the factor and character can not be converted and can not be calculated as well.**

# problem 2

```{r}
# install.packages("palmerpenguins")
# load penguins dataset 
data("penguins", package = "palmerpenguins")

# show the overall of the penguins
skimr::skim(penguins)

#the data in this dataset, including names/values of important variables. 
head(penguins)
```

**The variables of the penguins are `r names(penguins)`.**
**The data frame penguins has `r nrow(penguins)` rows.**
**The data frame penguins has `r ncol(penguins)` columns.**
**the species of this dataset, there are `r length(unique(penguins$species))` categories, which are  `r unique(penguins$species)`.**
**The island of this dataset, there are `r length(unique(penguins$island))` categories, which are `r unique(penguins$island)`.**
**The bill length (mm) starts from `r min(pull(penguins,bill_length_mm), na.rm = T)` to `r max(pull(penguins,bill_length_mm), na.rm = T)` with mean equals to `r mean(pull(penguins,bill_length_mm), na.rm = T)`.**
**The bill depth (mm) starts from `r min(pull(penguins,bill_depth_mm), na.rm = T)` to `r max(pull(penguins,bill_depth_mm), na.rm = T)` with mean equals to `r mean(pull(penguins,bill_depth_mm), na.rm = T)`.** 
**The flipper length (mm) starts from `r min(pull(penguins,flipper_length_mm), na.rm = T)` to `r max(pull(penguins,flipper_length_mm), na.rm = T)` with mean equals to `r mean(pull(penguins,flipper_length_mm), na.rm = T)`.** 
**The body mass (g) starts from `r min(pull(penguins,body_mass_g), na.rm = T)` to `r max(pull(penguins,body_mass_g), na.rm = T)` with mean equals to `r mean(pull(penguins,body_mass_g), na.rm = T)`.** 
  
* make the scatterplot 

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() + 
  ggtitle("Penguins Flipper length vs Bill length") + 
  ylab("Flipper length") +
  xlab("Bill length")

#save the plot
ggsave("scatter_plot.jpeg", height = 4, width = 4)
```




